### 2021-10-28 manuscript/hiv-gwas.tex

\begin{figure}[H]
	\centering
		\includegraphics[width=\linewidth]{figures/poumm_parameter_estimates.png}
		\caption{Marginal posterior distributions.}
\label{fig:poumm-parameters}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width = 0.7\linewidth]{figures/spvl_on_tree.png}
	\caption{Inferred HIV-1 $pol$ gene phylogeny with tips colored by (A) calculated spVL, (B) estimated non-pathogen effects on spVL and (C) estimated pathogen effects on spVL.}
	\label{fig:spvl-on-tree}
	\end{center}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
		\includegraphics[width=\linewidth]{figures/poumm_parameter_estimates.png}
		\caption{Posterior distributions compared to the prior for POUMM parameter estimates based on Swiss data. We ran two different MCMC chains to ensure the estimates converged. The black point on the x-axis shows the posterior mean value, which was used to estimate the pathogen- and non-pathogen effects on spVL.}
\label{fig:poumm-parameters}
\end{figure}

\begin{figure}[H]
\begin{center}
\includegraphics[width = \linewidth]{figures/spvl_on_tree.png}
	\caption{Inferred HIV-1 $pol$ gene phylogeny with tips colored by (A) calculated spVL, (B) estimated non-pathogen effects on spVL and (C) estimated pathogen effects on spVL.}
	\label{fig:spvl-on-tree}
	\end{center}
\end{figure}
